### 2020-12-22 HBtos/article/tikzpictures/figure11.tex

\documentclass{standalone}

\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{matrix}
\usetikzlibrary {shapes.geometric}
\usetikzlibrary {positioning}
\usetikzlibrary {decorations.pathmorphing}
\usetikzlibrary {arrows.meta}

\begin{document}
        \begin{tikzpicture}

            % \draw [help lines] (0,0) grid (13,6);

            \path   (5,4) node (a) [circle,draw,] {1}
                    (4,3) node (b) [circle,draw,fill = blue] {1}
                    (6,3) node (c) [circle,draw,] {1}
                    (3,2) node (d) [circle,draw,] {1}
                    (5,2) node (e) [circle,draw,fill = blue] {2}
                    (7,2) node (f) [circle,draw,] {1}
                    (2,1) node (g) [circle,draw,] {1}
                    (4,1) node (h) [circle,draw,] {3}
                    (6,1) node (i) [circle,draw,fill = blue] {3}
                    (8,1) node (j) [circle,draw,] {1}
                    (1,0) node (k) [circle,draw,] {1}
                    (3,0) node (l) [circle,draw,] {4}
                    (5,0) node (m) [circle,draw,fill = red] {6}
                    (7,0) node (n) [circle,draw,] {4}
                    (9,0) node (o) [circle,draw,] {1};

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =b ) -- (node cs:name =d);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =d ) -- (node cs:name =g);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =c ) -- (node cs:name =e);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =c ) -- (node cs:name =f);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =g ) -- (node cs:name =k);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =g ) -- (node cs:name =l);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =d ) -- (node cs:name =h);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =h ) -- (node cs:name =l);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =e ) -- (node cs:name =h);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =h ) -- (node cs:name =m);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =e ) -- (node cs:name =i);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =i ) -- (node cs:name =m);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =i ) -- (node cs:name =n);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =f ) -- (node cs:name =i);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =f ) -- (node cs:name =j);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=red]},red] (node cs: name =j ) -- (node cs:name =n);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=blue]},blue] (node cs: name =j ) -- (node cs:name =o);

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =a ) -- (0,4);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =b ) -- (0,3);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =d ) -- (0,2);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =g ) -- (0,1);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =k ) -- (0,0);

            \node [left=4.1cm,text width=2cm] at (a)
            {
            \mbox{\Large n = 0}
            };

            \node [left=3.1,text width=2cm] at (b)
            {
            \mbox{\Large n = 1}
            };

            \node [left=2.1,text width=2cm] at (d)
            {
            \mbox{\Large n = 2}
            };

            \node [left=1.1,text width=2cm] at (g)
            {
            \mbox{\Large n = 3}
            };

            \node [left=0.1,text width=2cm] at (k)
            {
            \mbox{\Large n = 4}
            };

            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =a ) -- (6,5);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =c ) -- (7,4);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =f ) -- (8,3);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =j ) -- (9,2);
            \draw[arrows = -{Triangle[open, angle=60:2mm,fill=black]}] [dash pattern=on 2pt off 2pt](node cs: name =o ) -- (10,1);

            \node [right=1cm,text width=1cm , rotate = 45] at (5,5)
            {
            \mbox{ k = 0}
            };

            \node [right=1cm,text width=1cm , rotate = 45] at (6,4)
            {
            \mbox{ k = 1}
            };

            \node [right=1cm,text width=1cm , rotate = 45] at (7,3)
            {
            \mbox{ k = 2}
            };

            \node [right=1cm,text width=1cm , rotate = 45] at (8,2)
            {
            \mbox{ k = 3}
            };

            \node [right=1cm,text width=1cm , rotate = 45] at (9,1)
            {
            \mbox{ k = 4}
            };

        \end{tikzpicture}
\end{document}