### 2020-12-23 HBtos/article/tikzpictures/figure4.tex

\documentclass{standalone}
\usepackage{tikz}
\usepackage{amsmath}
\usetikzlibrary{matrix}
\usetikzlibrary {shapes.geometric}
\usetikzlibrary {arrows.meta}
\begin{document}
        \begin{tikzpicture}[ultra thick]

            %\draw [help lines] (0,0) grid (10,10);

            \path   (5,10)  node (a) [circle,draw] {A}
                    (3,9) node (b) [circle,draw] {B}
                    (7,9) node (c) [circle,draw] {C}
                    (2,8) node (d) [circle,draw] {D}
                    (4,8) node (e) [circle,draw] {E}
                    (6,8) node (f) [circle,draw] {F}
                    (8,8) node (g) [circle,draw] {G};

            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red]  (node cs: name =a ) -- (node cs:name =b);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =a ) -- (node cs:name =c);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =b ) -- (node cs:name =d);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =b ) -- (node cs:name =e);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = red]},red] (node cs: name =c ) -- (node cs:name =f);
            \draw[arrows = -{Triangle[open,angle=60:2mm,fill = blue]},blue] (node cs: name =c ) -- (node cs:name =g);

        \end{tikzpicture}
\end{document}